QPLIB: A Library of Quadratic Programming Instances

### 2017-01-30 QPLIB-2.2.tex
remove extra z, add top
- see issue #4, https://github.com/fabiofurini/QPLIB/issues/4#issuecomment-276062961

When a $Q^i$ is positive semidefinite (PSD), i.e., the corresponding constraint/objective function is convex, general quadratic constraints are in fact equivalent to diagonal ones. In fact, since every PSD matrix can be factorized as $Q^i = L^i (L^i)^\top$, e.g.~by the (incomplete) Cholesky factorization, $f^i(x) = x^\top Q^i x = \sum_{j \in \Mcn} z^2_jz$ where $z = x^\top L^i$. Hence, one could think that D** problems need not be distinguished from C** ones; however, this is true only for ``complicated'' constraints, but not for ``simple'' ones, because the above reformulation technique introduces linear constraints. Indeed, while C*L (and, a fortiori, C*\{C,Q\}) can always be brought to D*L (D*\{C,Q\}), using the same technique C*B becomes D*L, which is significantly different from D*B. In practice, a diagonal convex objective function under linear constraints is found in many applications (e.g., \cite{FrFG16,FrGe06a,FrGe09a,FGGP11}), so that D*L still makes sense to distinguish the case where the objective function is ``naturally'' separable from that where separability is artificially introduced.

>>>>

When a $Q^i$ is positive semidefinite (PSD), i.e., the corresponding constraint/objective function is convex, general quadratic constraints are in fact equivalent to diagonal ones. In fact, since every PSD matrix can be factorized as $Q^i = L^i (L^i)^\top$, e.g.~by the (incomplete) Cholesky factorization, $f^i(x) = x^\top Q^i x = \sum_{j \in \Mcn} z^2_j$ where $z^\top = x^\top L^i$. Hence, one could think that D** problems need not be distinguished from C** ones; however, this is true only for ``complicated'' constraints, but not for ``simple'' ones, because the above reformulation technique introduces linear constraints. Indeed, while C*L (and, a fortiori, C*\{C,Q\}) can always be brought to D*L (D*\{C,Q\}), using the same technique C*B becomes D*L, which is significantly different from D*B. In practice, a diagonal convex objective function under linear constraints is found in many applications (e.g., \cite{FrFG16,FrGe06a,FrGe09a,FGGP11}), so that D*L still makes sense to distinguish the case where the objective function is ``naturally'' separable from that where separability is artificially introduced.
